Compositional equivalences based on Open pNets

### 2020-07-20 2016-Weak-FH-Bisim/WeakBisim.tex
petite relecture intro

This article defines bisimulation relations for the pNet model for the comparison of systems specified as pNets.
 We first define a strong bisimulation for open pNets.
  In practice, as happens in process algebras, strong bisimulation is too strong, and
  we need to define some coarser relations, taking into account
  invisible or internal moves.
  We then define an equivalence relation similar to
  the classical \emph{weak bisimulation}, and study its properties.
Among these properties we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
The article is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.
\end{abstract}

@@

We develop here a semantics for a model of interacting processes with parameters and holes. 
The main interest of our symbolic approach is to define a method to
prove properties directly on open structures, that will be preserved
by any correct instantiation of the holes.
As a consequence, our model allows us to reason on composition
operators as well as on full-size distributed systems. The parametric
nature of the model and the properties of compositionability of the
equivalence relations thus play a major role here and are the main
strengths of  our contribution.

>>>>

This article defines bisimulation relations  for the comparison of systems specified as pNets.
 We first define a strong bisimulation for open pNets.
  In practice, as happens in process algebras, strong bisimulation is too strong, and
  we need to define some coarser relations, taking into account
  invisible or internal moves.
  We then define an equivalence relation similar to
  the classical \emph{weak bisimulation}, and study its properties.
Among these properties we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
The article is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.
\end{abstract}

@@

We develop here a semantics for a model of interacting processes with parameters and holes. 
The main interest of our symbolic approach is to define a method to
prove properties directly on open structures; these properties will then be preserved
by any correct instantiation of the holes.
As a consequence, our model allows us to reason on composition
operators as well as on full-size distributed systems. The parametric
nature of the model and the properties of compositionability of the
equivalence relations thus play a major role here and are the main
strengths of  our contribution.
